The GALEX View of ``Boyajian's Star''

### 2017-10-15 paper/paper.tex
a couple changes from Manuel

To determine what the typical variation in NUV flux is for F stars, we compared the GALEX GR6 and GCK measurements for over 140,000 \Kepler stars found in both datasets. Note the original GALEX GR6 data was not available over the entire Kepler footprint, and was not taken over a single observing window 2011 for all targets as for KIC 8462852. The timescales between GR6 and GCK visits may therefore vary widely. A full analysis of this comparison, while beyond the scope of our work here, is underway (M. Olmedo et al. in preparation). With this large comparison set we found that stars with temperatures near KIC 8462852 (6750 K) have an average variation between these two epochs of 2.5\%. The 3.5\% NUV variation seen for KIC 8462852 is therefore significant and believable, but not necessarily abnormal for stars of this spectral type.

>>>>

%To determine what the typical variation in NUV flux is for F stars, we compared the GALEX GR6 and GCK measurements for over 140,000 \Kepler stars found in both datasets. Note the original GALEX GR6 data was not available over the entire Kepler footprint, and was not taken over a single observing window 2011 for all targets as for KIC 8462852. The timescales between GR6 and GCK visits may therefore vary widely. A full analysis of this comparison, while beyond the scope of our work here, is underway (M. Olmedo et al. in preparation). With this large comparison set we found that stars with temperatures near KIC 8462852 (6750 K) have an average variation between these two epochs of 2.5\%. The 3.5\% NUV variation seen for KIC 8462852 is therefore significant and believable, but not necessarily abnormal for stars of this spectral type.

To determine what the typical variation in NUV flux is for F stars, we analyzed the variability for over 140,000 GCK stars in common with the Kepler Stellar Catalog \citep{mathur2017}, observed on average 15 times over a time interval of 40 days in 2012. Note the original GALEX data was not available over the entire Kepler footprint, and was not taken over a single 70 day observing window 2011 for all targets as for KIC 8462852. A full analysis of this variability, while beyond the scope of our work here, is underway (Daniel  Olmedo et al. in preparation). We found that stars with temperatures near KIC 8462852 (6750 K) have an average variation of 2.5\%. The 3.5\% NUV variation seen for KIC 8462852 is therefore significant and believable, but not necessarily abnormal for stars of this spectral type. “
